 \documentclass[subfiles.tex]{subfiles}

%%% Paquetes necesarios: no borrar por favor

\usepackage[spanish]{babel}
%%%%%%%%%%%%title%%%%%%%%%%%
\makeatletter
\def\email#1{\def\@email{#1}}
\def\address#1{\def\@address{#1}}
\def\thanks#1{\def\@thanks{#1}}
\def\maketitle{
	\begin{titlepage}
	\null\vfill
	\begin{center}
		{\LARGE \@title}
		\vskip 1cm
		{\Large \@author}
		\vskip 1cm
		{\texttt{\@email}}
		\vskip 1cm
		{\texttt{\@address}}
		\vskip 1cm
		{\Large \@date}
		\vskip 1cm
		{\tiny \@thanks}
		
	\end{center}
	\vfill\null
	\end{titlepage}
}

\makeatother

%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{hyperref}
\hypersetup{
    colorlinks=false,
    linkcolor=black,
    citecolor=black,
    filecolor=black,
    urlcolor=black
}
\usepackage[all]{xypic}
\usepackage{amssymb}


%%% Tamano pagina: no cambiar por favor




%%% Titulo pagina: no cambiar por favor

\newcommand{\header}{
 \hrule
 \vskip 6truept
 \centerline{\large X Encuentro Internacional de Matem\'aticas}
  \centerline{EIMAT}
  \centerline{Barranquilla - Colombia}
  \centerline{30 Septiembre al 03 Ocutbre, 2014}
 \vskip 6truept
 \hrule
 \vspace{0.1cm}
 }

%%%  Titulo del resumen

\title{ \header Bounded mild solutions to fractional integro-differential equations in Banach spaces}


%%%  Nombres y datos de los autores

\author{Rodrigo Ponce}
\address{Universidad de Talca
\\ email: \href{mailto:rponce@inst-mat.utalca.cl}{{\rm rponce@inst-mat.utalca.cl}}.
}
\thanks{Research was supported by Fondecyt-Iniciaci\'on 11130619}


\thispagestyle{empty}
\begin{document}
\maketitle
%\thispagestyle{empty}

%%% Breve abstract

\begin{abstract}
We study the
existence and uniqueness of bounded solutions for a semilinear fractional
differential equation. Sufficient conditions are established for the
existence and uniqueness of an almost periodic, almost automorphic
and asymptotically almost periodic solution, among other.
\end{abstract}
\vspace{1cm}

%%% Texto del resumen, de a lo m\'as 2 paginas
In this  talk, we consider the following semilinear fractional differential equation with infinite delay
\begin{equation}\label{eq1.1}
\displaystyle D^\alpha u(t) = Au(t)+\int_{-\infty}^t a(t-s)Au(s)ds +f(t,u(t)), \qquad t\in\mathbb{R},
\end{equation}
where $A$  is a closed linear
operator defined on a Banach space $X,$ $a\in L^1(\mathbb{R}_+)$ is a scalar-valued kernel, $f$ belongs to a closed
subspace of the space of continuous and bounded functions, and for $\alpha>0,$ the fractional derivative is understood in the Weyl's sense.

Under appropriate assumptions on $A$ and $f,$ we want to prove that (\ref{eq1.1}) has a unique {\it mild} solution $u$ which behaves in the same way that $f$. For example, we want to find conditions implying that $u$ is almost periodic (resp.
automorphic) if $f(\cdot,x)$ is almost periodic (resp. almost
automorphic). Existence of almost periodic or almost automorphic (among other) mild solutions to equations in the form of (\ref{eq1.1}) has been studied, for instance, in \cite{Cu-Li08,Di-09,Di-Ng-VMi-04} .

Using some results in \cite{Li-Ng-09}, we study in \cite{Pon-13} the existence and uniqueness of mild solutions for (\ref{eq1.1}) where the input data $f$ belongs to some of above functions spaces. Concretely, we prove that if $f$ is for example almost periodic (resp. almost automorphic) and satisfies some Lipschitz type conditions, then there exists a unique mild solution $u$ of (\ref{eq1.1}) which is almost periodic (resp. almost automorphic) and is given by
\begin{equation}\label{eq1.2}
u(t)=\int_{-\infty}^t S_\alpha(t-s)f(s,u(s))ds, \quad t\in\mathbb{R},
\end{equation}
where $\{S_\alpha(t)\}_{t\geq 0}$ is the $\alpha$-{\it resolvent family} generated by $A$. It is remarkable that, in the scalar case, that is $A=-\rho I,$ with $\rho>0,$ some concrete examples of integrable $\alpha$-resolvent families are showed.




%\vspace{3cm}

%%% Referencias: seguir el formato sugerido por favor

\begin{thebibliography}{99}

%\bibitem{tpp}
%N1.~Apellido1, N2.~Apellido2:
%{\em T\'itulo articulo}, nombre revista, n\'umero, p\'agina inicial--p\'agina final, a\~no.


\bibitem{Cu-Li08} C. Cuevas, C. Lizama. {\it Almost Automorphic Solutions to a class of Semilinear Fractional Differential Equations,} Applied Math. Letters, {\bf 21}, (2008), 1315-1319.%8

\bibitem{Di-09} T. Diagana. {\it Existence of solutions to some classes of partial fractional differential equations,} Nonlinear Anal. {\bf 71} (2009), 5269-5300.%13

\bibitem{Di-Ng-VMi-04} T. Diagana, G. M. N'Gu\'er\'ekata, N. van Minh. {\it Almost automorphic solutions of evolution equations,} Proc. Amer. Math. Soc. {\bf 132} (11) (2004), 3289-3298.%14

\bibitem{Li-Ng-09}  C. Lizama, G. M. N'Gu\'er\'ekata. {\it Bounded mild solutions for semilinear integro-differential equations in Banach spaces,} Integral Equations and Operator Theory, {\bf 68} (2) (2010), 207-227.

\bibitem{Pon-13} R. Ponce, {\it Bounded mild solutions to fractional integro-differential equations in Banach spaces,} Semigroup Forum, 87, (2013), 377-392, DOI 10.1007/s00233-013-9474-y.

\end{thebibliography}
 \end{document} 
